---
title: "UChi MS-ADS Whole Code"
author: "Yiduan Zheng"
date: "2023-12-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Original Prompt (Econometrics Problem Set)

This problem is about ``Do College Graduates Serving as Village Officials Help Rural China?'' by Guojun He and Shaoda Wang, published in American Economic Journal: Applied Economics in 2017 (He and Wang (2017)). Try to reproduce Figure 2 of the paper. Then, produce a version of Figure 2 that uses the imputation procedure. Discuss the extent to which the two versions agree and differ in their substantive conclusions.

```{r}
## load libraries here
library(pacman)
p_load(ggplot2, dplyr, magrittr, sandwich, stats, car, lmtest, haven, ivreg, 
       MASS, ivmte, ggpubr, stargazer, tidyverse, tidyr, broom, xtable)
       
rm(list = ls())
```

```{r}
hewang <- read.csv("hewang2017.csv")
View(hewang)
```

```{r}
# step 0: generate event time
hewang.cal <- hewang %>%
  group_by(village) %>%
  mutate(tyear = year[which(cgvo == 1)[1]]) %>%
  replace_na(list(tyear = Inf))
```

```{r}
# step 1: generate relative time
hewang.rel <- hewang.cal %>%
  mutate(relyear = year - tyear,
         relyear = replace(relyear, relyear <= -4, -4),
         relyear = replace(relyear, relyear >= 3, 3))
```

```{r}
# step 2: convert to factors and relevel to -1
hewang.rel %<>% 
  mutate(relyear.num = relyear,
         relyear = as.factor(relyear),
         relyear = fct_relevel(relyear, "-1"))
```

```{r}
# note: village 28 is an always-treated village and thus should not be included
# I have filtered it out for this purpose
# to better align with the original, just use hewang.rel
hewang.rel.alt <- hewang.rel %>% filter(village != 28)
```

```{r}
# set up vectors here
Y <- c("l_subsidy_rate", "l_poor_housing_rate", 
       "l_poor_reg_rate", "l_disability_rate")

title.letter.lab <- c("A", "B", "C", "D")
title.lab <- c("subsidized population", "poor-quality housing", 
               "registered poor households", "people with disabilities")
x.lab <- c("<= -4", "-3", "-2", "", "0", "1", "2", ">= 3")
```

```{r}
fstat <- c()
plot <- list()
table <- list()
```

```{r}
# this is recovering the original table

for (i in 1:4) {
  # run the regression
  fmla.ori <- formula(paste0(Y[i]," ~
       as.factor(village) + as.factor(year) + relyear"))
  
  lr.ori <- lm(data = hewang.rel.alt, fmla.ori)
  
  ftest <- (names(lr.ori$coeff) %in% paste0("relyear", -4:-2))
  vc <- vcovCL(lr.ori, cluster = ~district, type ="HC0")
  fstat[i] <- linearHypothesis(lr.ori, ftest, vcov. = vc)[2,"Pr(>F)"]
  
  # get cluster SE and filter
  plotdf <- lr.ori %>%
    tidy() %>%
    mutate(std.error = sqrt(diag(vc))) %>%
    filter(str_detect(term, "relyear")) %>%
    mutate(term = as.numeric(str_replace(term, "relyear", ""))) 
     
  # third, save table
  table[[i]] <- plotdf
  
  # last, we plot
  plot[[i]] <- 
    ggplot(data = plotdf, aes(x = term, y = estimate, 
                              ymin = estimate - qnorm(0.95)*std.error, 
                              ymax = estimate + qnorm(0.95)*std.error)) +
    theme_bw() +
    geom_point(shape = 23, size = 3) +
    geom_errorbar() +
    geom_hline(aes(yintercept = 0), linetype = 5) +
    geom_vline(aes(xintercept = -1), linetype = 5) +
    scale_x_continuous(
      breaks = min(plotdf$term):max(plotdf$term),
      labels = x.lab) +
    labs(x = "Relative Time", 
         y = "Estimated Coefficients",
         title = paste0("Panel ", title.letter.lab[i], 
                        ". Effect on ", title.lab[i]))
  
}

fstat
# [1] 0.25478749 0.84897316 0.80318982 0.08530861
# all are insignificant at 5%
```

```{r}
# original graph
ggarrange(plot[[1]], plot[[2]], plot[[3]], plot[[4]], ncol = 2, nrow = 2)
```

```{r}
# now we start imputing
# first create the reltime.pos variable and adjust others
hewang.rel.alt %<>% mutate(
  relyear.pos = ifelse(relyear.num >= 0, relyear.num, -1),
  relyear.pos = as.factor(relyear.pos),
  year.num = year,
  year = as.factor(year),
  year = fct_relevel(year, "2000"),
  tyear.num = tyear,
  tyear = as.factor(tyear),
  tyear = fct_relevel(tyear, "Inf")
)
```

```{r}
# cancel the group effect from previous code
hewang.rel.alt %<>% ungroup()
```

```{r}
# imputation function
# code partially borrowed from lecture notes
imputation <- function(data.in, Y) {
    # the data is structured such as some variables are consistently uncollected 
    # for some years, so restrict dataframe to avoid errors
    data.temp <- data.in %>% filter(!is.na(!!sym(Y))) 
    fmla1 <- formula(paste0(Y, " ~ year + tyear"))
    
    # Step one
    lr.imp <- lm(data = data.temp %>% filter(relyear.num < 0), fmla1)
    if (Y == "l_disability_rate"){
      # this is the only always-treated unit after filtering for disability rate
      data.temp %<>% filter(village != 176)
    }
    
    # Step two
    data.temp %>% 
      mutate(y.imp := !!sym(Y) - predict(lr.imp, newdata = data.temp)) %>%
      lm(formula = y.imp ~ relyear.pos)
}
```

```{r}
# Bootstrap the post-period
villages <- unique(hewang.rel.alt$village)
nv <- length(villages)
nbs <- 100
```

```{r}
# bootstrap
impute.bs.se <- function(Y, nbs = 500){
  bs.out <- vector(mode = "list", length = nbs)
  
  for (i in 1:nbs) { # cluster bootstrap
    sample(villages, nv, replace = TRUE) %>%
      lapply(function(v) hewang.rel.alt %>% 
               filter(village == v)) %>%
      bind_rows() %>%
      imputation(., Y) %>%
      tidy() %>%
      pull("estimate", name = term)-> bs.out[[i]]
  }
  bs <- simplify2array(bs.out)
  bs <- bs - rowMeans(bs)
  bs <- t(bs)
  vc <- (1 / nbs) * (t(bs) %*% bs) 
  bs.se <- sqrt(diag(vc))
  return(bs.se)
}
```

```{r}
table.imp <- list()
plot.imp <- list()
```

```{r}
# readjust, since the factor seems to cancel out somewhere
hewang.rel.alt %<>% mutate(relyear = as.factor(relyear))
```

```{r}
for (i in 1:length(Y)){
  data.temp <- hewang.rel.alt %>% filter(!is.na(!!sym(Y[i]))) 
  
  fmla1 <- formula(paste0(Y[i], " ~ year + tyear + relyear"))
  lr <- lm(data = data.temp %>% filter(relyear.num < 0), fmla1)

  lr %>%
  tidy() %>%
  filter(!is.na(estimate)) %>%
  mutate(std.error = sqrt(diag(vcovCL(lr, cluster = ~district, type ="HC0")))) %>%
  bind_rows(., hewang.rel.alt %>% 
              imputation(Y[i]) %>% 
              tidy() %>% 
              mutate(std.error = impute.bs.se(Y = Y[i]))) %>%
  filter(str_detect(term, "relyear")) %>%
  mutate(
    relyear = str_replace(term, "relyear", ""),
    relyear = str_replace(relyear, ".pos", ""),
    relyear = as.numeric(relyear),
    cilb = estimate - qnorm(0.95) * std.error,
    ciub = estimate + qnorm(0.95) * std.error
  ) -> lr.df

  # save table
  table.imp[[i]] <- lr.df
  
  # save plot
  plot.imp[[i]] <- 
    ggplot(data = lr.df, aes(x = relyear, y = estimate, 
                             ymin = cilb, ymax = ciub)) +
    theme_bw() +
    geom_point(shape = 1, size = 3) +
    geom_errorbar() +
    geom_hline(aes(yintercept = 0), linetype = 5) +
    geom_vline(aes(xintercept = -1), linetype = 5) +
    scale_x_continuous(
      breaks = min(lr.df$relyear):max(lr.df$relyear),
      labels = x.lab) +
    labs(x = "Relative Time", 
         y = "Estimated Coefficients",
         title = paste0("Panel ", title.letter.lab[i], 
                        ". Effect on ", title.lab[i]))
}
```

```{r}
# imputed graph
ggarrange(plot.imp[[1]], plot.imp[[2]], plot.imp[[3]], plot.imp[[4]], ncol = 2, nrow = 2)
```



















